---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QBootTest

<!-- badges: start -->
<!-- badges: end -->

The goal of QBootTest is to conduct multiplier bootstrap tests for high-dimensional quantile regression

## Installation

You can install the development version from GitHub:

```{r, message=FALSE, warning=FALSE}
install.packages("remotes")
remotes::install_github("havanashw/QBootTest")
```

## Example

### Asymptotic p-value

```{r}
library(QBootTest)
library(MASS)

set.seed(1)
n <- 80; p <- 50
beta.true <- rep(1, p)
Sig <- toeplitz(0.5^seq(0, p-1))
error <- rnorm(n)
x <- mvrnorm(n, mu=rep(0, p), Sigma=Sig)
y <- x%*%beta.true + error

QBootTest(x, y, tau = 0.5, method = "asymptotic")
```

### Multiplier bootstrap p-value

```{r}
QBootTest(x, y, tau = 0.5, method = "bootstrap", multiplier = "gaussian", M = 200)
```

### Return test statistic and bootstrap draws (optional)

If you want the test statistic and bootstrap replicates for plots, use `return_details = TRUE`:

```{r}
res <- QBootTest(x, y, tau = 0.5, method = "bootstrap", 
                 multiplier = "rademacher", M = 200,
                 return_details = TRUE)
str(res, max.level = 1)
```

## Notes

1. $x$ should be an $n \times p$ numeric matrix and $y$ is an $n$ numeric vector.

2. Use `scale = TRUE` if you want to standardize $x$ and $y$ before computing the test.
